---
title: "_12_4_Popups_DataVisualizationGisLeaflet"
author: "Sobil"
date: "14/11/2019"
output: html_document
---

Popups-

1 > Popup with no closeButton

```{r}
library(leaflet)
content <- paste(sep = "<br/>",
  "<b><a href='https://github.com/sobil-dalal/R_DataCamp'>Sobil GitHub R Repositry</a></b>",
  "Sobil Dalal",
  "Gurugram Haryana"
)

m <- leaflet() %>% addTiles() %>%
  addPopups(lng =  77.026634,lat = 28.459497, content,
    options = popupOptions(closeButton = FALSE)
  )
m
```

2 > Popups and Lables on markers

```{r}
library(htmltools)

df <- read.csv(textConnection(
"Name,Lat,Long
Samurai Noodle,47.597131,-122.327298
Kukai Ramen,47.6154,-122.327157
Tsukushinbo,47.59987,-122.326726"
))

m <- leaflet(df) %>% 
  addTiles() %>%
  addMarkers(~Long, ~Lat, popup = ~htmlEscape(df$Name), label = ~htmlEscape(Lat))
m
```

3 > Customizing Marker Labels

```{r}
# Change Text Size and text Only and also a custom CSS
m <- leaflet() %>% 
  addTiles() %>% 
  setView(-118.456554, 34.09, 13) %>%
  addMarkers(
    lng = -118.456554, lat = 34.105,
    label = "Default Label",
    labelOptions = labelOptions(noHide = T)) %>%
  addMarkers(
    lng = -118.456554, lat = 34.095,
    label = "Label w/o surrounding box",
    labelOptions = labelOptions(noHide = T, textOnly = TRUE)) %>%
  addMarkers(
    lng = -118.456554, lat = 34.085,
    label = "label w/ textsize 15px",
    labelOptions = labelOptions(noHide = T, textsize = "15px")) %>%
  addMarkers(
    lng = -118.456554, lat = 34.075,
    label = "Label w/ custom CSS style",
    labelOptions = labelOptions(noHide = T, direction = "bottom",
      style = list(
        "color" = "red",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )))
m
```

4 > Labels without markers
You can create labels without the accompanying markers using the addLabelOnlyMarkers function.

```{r}
m <- leaflet() %>% 
  addTiles() %>% 
  setView(-118.456554, 34.09, 13) %>%
  addLabelOnlyMarkers(
    lng = -118.456554, lat = 34.105,
    label = "Default Label",
    labelOptions = labelOptions(noHide = T)) %>%
  addLabelOnlyMarkers(
    lng = -118.456554, lat = 34.095,
    label = "Label w/o surrounding box",
    labelOptions = labelOptions(noHide = T, textOnly = TRUE)) %>%
  addLabelOnlyMarkers(
    lng = -118.456554, lat = 34.085,
    label = "label w/ textsize 15px",
    labelOptions = labelOptions(noHide = T, textsize = "15px")) %>%
  addLabelOnlyMarkers(
    lng = -118.456554, lat = 34.075,
    label = "Label w/ custom CSS style",
    labelOptions = labelOptions(noHide = T, direction = "bottom",
      style = list(
        "color" = "red",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )))
m
```



The "leaflet" R package is copyright © 2014-2016 RStudio, Inc.
The Leaflet JavaScript library is © 2010–2016 Vladimir Agafonkin, 2010–2011 CloudMade.
Maps © OpenStreetMap contributors unless otherwise noted.
Content from - https://rstudio.github.io/
