---
title: "_12_2_MapWidgets_DataVisualizationGisLeaflet"
author: "Sobil"
date: "13/11/2019"
output: html_document
---

Contains content from rstudio.github.io site

Initializing Options
# Set value for the minZoom and maxZoom settings.
leaflet(options = leafletOptions(minZoom = 0, maxZoom = 18))

Map Methods
setView() sets the center of the map view and the zoom level;
fitBounds() fits the view into the rectangle [lng1, lat1] – [lng2, lat2];
clearBounds() clears the bound, so that the view will be automatically determined by the range of latitude/longitude data in the map layers if provided;

The Data Object
Both leaflet() and the map layer functions have an optional data parameter that is designed to receive spatial data in one of several forms:

I > From base R:
lng/lat matrix
data frame with lng/lat columns

II > From the sp package:
SpatialPoints[DataFrame]
Line/Lines
SpatialLines[DataFrame]
Polygon/Polygons
SpatialPolygons[DataFrame]

III > From the maps package:
the data frame from returned from map()

Let's start with - 

I > From base R:

  Part 1 - Create a data frame with lat, long, and add onto the leaflet layer

```{r echo=FALSE}
library(leaflet)
df <- data.frame(lat = 17:27, long = rnorm(11, 77, 3))
m <- leaflet(df) %>% 
  addTiles() %>%
  addCircles()
m
```

  Part 2 - Create a data frame with lat, long, and add onto the leaflet layer and explicitly mention the column to be referred for lat, long

```{r echo=FALSE}
df <- data.frame(lat = 17:27, long = rnorm(11, 77, 3))
m <- leaflet(df) %>% 
  addTiles() %>%
  addCircles(lng = ~long, lat = ~lat)
m
```

  Part 3 - Create a data frame with lat, long, and add onto the map layer (we can overide or add the data onto map)

```{r echo=FALSE}
df <- data.frame(lat = 17:27, long = rnorm(11, 77, 3))
df2 <- data.frame(lat = 27:37, long = rnorm(11, 77, 3))
m <- leaflet(df) %>% 
  addTiles() %>%
  addCircles(data = df2, lng = ~long, lat = ~lat)
m
```

II > From the sp package:
  Install the "sp" package : install.packages("sp")
  
  Note - if you get a error of rgeos package not found, run the below commoand on console install.packages("rgeos")
  
```{r}
library(sp)
p1 = Polygon(cbind(c(2, 4, 4, 1, 2), c(2, 3, 5, 4, 2)))
p2 = Polygon(cbind(c(5, 4, 2, 5), c(2, 3, 2, 2)))
p3 = Polygon(cbind(c(4, 4, 5, 10, 4), c(5, 3, 2, 5, 5)))
p4 = Polygon(cbind(c(5, 6, 6, 5, 5), c(4, 4, 3, 3, 4)), hole = TRUE)
ps1 = Polygons(list(p1), "s1")
ps2 = Polygons(list(p2), "s2")
ps3 = Polygons(list(p4, p3), "s3/4")
spP = SpatialPolygons(list(ps1, ps2, ps3), 1:3)
m <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = spP)
m
```
  
III > From the maps package:

```{r}
library(maps)
mapStates = map("state", fill = TRUE, plot = FALSE)
m <- leaflet(data = mapStates) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = 0.7), stroke = TRUE)
m
```



The Formula Interface
The arguments of all layer functions can take normal R objects, such as a numeric vector for the lat argument, or a character vector of colors for the color argument. They can also take a one-sided formula, in which case the formula will be evaluated using the data argument as the environment. For example, ~ x means the variable x in the data object, and you can write arbitrary expressions on the right-hand side, e.g., ~ sqrt(x + 1).

```{r}
m = leaflet() %>% addTiles()
df = data.frame(
  lat = rnorm(100),
  lng = rnorm(100),
  size = runif(100, 5, 20),
  color = sample(colors(), 100)
)
m = leaflet(df) %>% 
  addTiles() %>% 
  addCircleMarkers(radius = ~size, color = ~color, fill = FALSE) 
m
```



The "leaflet" R package is copyright © 2014-2016 RStudio, Inc.
The Leaflet JavaScript library is © 2010–2016 Vladimir Agafonkin, 2010–2011 CloudMade.
Maps © OpenStreetMap contributors unless otherwise noted.
Content from - https://rstudio.github.io/
