---
title: "_12_4_Markers_DataVisualizationGisLeaflet.Rmd"
author: "Sobil"
date: "13/11/2019"
output: html_document
---

Data sources
Point data for markers can come from a variety of sources:

SpatialPoints or SpatialPointsDataFrame objects (from the sp package)
POINT, sfc_POINT, and sf objects (from the sf package); only X and Y dimensions will be considered
Two-column numeric matrices (first column is longitude, second is latitude)
Data frame with latitude and logitude columns. You can explicitly tell the marker function which columns contain the coordinate data (e.g. addMarkers(lng = ~Longitude, lat = ~Latitude)), or let the function look for columns named lat/latitude and lon/lng/long/longitude (case insensitive).
Simply provide numeric vectors as lng and lat arguments
Note that MULTIPOINT objects from sf are not supported at this time.

Icon Markers

```{r}
library(leaflet)
m <- leaflet(data = quakes[140:160,]) %>% 
  addTiles() %>%
  addMarkers(~long, ~lat, popup = ~as.character(mag), label = ~as.character(mag))
m
```

Awesome Icons
Leaflet supports even more customizable markers using the awesome markers leaflet plugin.

The addAwesomeMarkers() function is similar to addMarkers() function but additionally allows you to specify custom colors for the markers as well as icons from the Font Awesome, Bootstrap Glyphicons, and Ion icons icon libraries.

```{r}
df <- quakes[140:160,]

getColor <- function(quakes) {
  sapply(quakes$mag, function(mag) {
  if(mag <= 4) {
    "green"
  } else if(mag <= 5) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(df)
)

m <- leaflet(df) %>% 
  addTiles() %>%
  addAwesomeMarkers(~long, ~lat, icon=icons, label=~as.character(mag))
m
```

Circle Markers

```{r}
m <- leaflet(df) %>% 
  addTiles() %>% 
  addCircleMarkers()
m
```




The "leaflet" R package is copyright © 2014-2016 RStudio, Inc.
The Leaflet JavaScript library is © 2010–2016 Vladimir Agafonkin, 2010–2011 CloudMade.
Maps © OpenStreetMap contributors unless otherwise noted.
Content from - https://rstudio.github.io/